\documentclass[a4paper, 12pt]{article}
\usepackage{TLCresume}
\begin{document}

%using zitemize instead of itemize will allow for tighter spacing before and after each line

%====================
% EXPERIENCE 1
%====================
%\vspace*{8pt}

\subsection {\href
{https://playrix.com/}
{Playrix}
\hfill 06 2020 - 04 2023}
\subtext{Test analyst \hfill Russia, Petrozavodsk}

\begin{zitemize}
\item Implemented an autotest log analysis system, which led to an 80\% increase in the number of errors detected by autotests and reduced the time to find and fix them.
\item Automated the processes of working with tasks in Asana, reducing the time spent on their processing.
This saved up to 10\% of the workday.
\item Improved the autotest development process by implementing typing and using docstring, which improved the quality of the code base and accelerated the adaptation of other employees.
\item Developed and maintained more than 50 UI autotests to test basic events, tutorials and match-3 in-game, using Python.
\item Provided coverage of about 10\% of the functional requirements on the project checklists with the help of developed autotests.
\end{zitemize}

\textbf {Tech stack}: Charles, Python, Git, Asana API, TeamCity


%====================
% EXPERIENCE 2
%====================
\vspace*{8pt}

\subsection{{Freelance } \hfill 08 2019 - 01 2020}
\subtext{Python developer \hfill Russia, Petrozavodsk}

\begin{zitemize}
\item Developed a telegram bot to view stock multiples of various companies.
\item Setup and deployed bot on Heroku.
\item Adding new functionality for the bot.
\end{zitemize}

\textbf {Tech stack}: Python, beautifulsoup4, matplotlib, pyTelegramBotAPI, Git

\end{document}
